### 2013-04-02 menger.tex
2-mark = k-mark for Menger Game finite player

@@

  \begin{question}
    Does $F \markwin \mengame{X}$ imply $X$ is $\sigma$-compact?
  \end{question}

>>>>

  \begin{lemma}
    Let $\sigma(\mc{U}, n)$ be a winning Markov strategy for $F$ in $\mengame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then for
      \[
        C_n = \bigcap_{\mc{U}\in\mathfrak{C}} \overline{\bigcup\sigma(\mc{U},n)}
      \]
    and
      \[
        D_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
      \]
    it follows that $\bigcup_{n<\omega} C_n = \bigcup_{n<\omega} D_n = X$.
  \end{lemma}

  \begin{proof}
    Observe $D_n \subseteq C_n$. Suppose that $x \not\in D_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)$ for any $n<\omega$. Then for each $n$, pick $\mc{U}_n\in\mathfrak{C}$ such that $x\not\in \bigcup\sigma(\mc{U}_n,n)$. Then $\sigma$ does not defeat the play $\mc{U}_0,\mc{U}_1,\dots$ since the $\sigma(\mc{U}_n,n)$ do not cover $x$, contradiction.
  \end{proof}

  \begin{theorem}
    For regular spaces $X$, $F \markwin \mengame{X}$ if and only if $X$ is $\sigma$-compact.
  \end{theorem}

  \begin{proof}
    The reverse implication has already been shown. To complete the proof, we look to Scheepers for inspiration.

    Let $\sigma(\mathcal{U},n)$ be a winning Markov strategy for $F$ in $\mengame{X}$. Let $\mathfrak{C}$ collect all open covers of $X$. Define
      \[
        C_n = \bigcap_{\mc{U}\in\mathfrak{C}} \overline{\bigcup\sigma(\mc{U},n)}
      \]
    as in the previous lemma. Note that $\bigcup_{n<\omega} C_n = X$, and we will show each $C_n$ is compact as it is $H$-closed.

    Let $\mc{U}$ be an open cover of $C_n$, and $\mc{V}$ be a cover of $X\setminus C_n$ by open sets whose closures are disjoint from $C_n$ (possible by regularity).

    Since $\mc{U}\cup\mc{V}$ covers $X$, $\overline{\bigcup\sigma(\mc{U}\cup\mc{V},n)} \supseteq C_n$. Furthermore, if $\mc{F} = \sigma(\mc{U}\cup\mc{V},n)\setminus \mc{V}$, then $\overline{\bigcup\mc{F}} \supseteq C_n$ (the closures of sets in $\mc{V}$ missed $C_n$). Thus $\mc{F}$ witnesses that $C_n$ is $H$-closed.
  \end{proof}

  \begin{example}
  Let $R$ be given the topology from example 63 from Counterexamples in Topology, the topology generated by open intervals with countable sets removed. This space is non-regular, non-$\sigma$-compact, and Lindel\"of. It is also Menger as $F \win \mengame{R}$, but $F \not\markwin \mengame{R}$.
  \end{example}

  \begin{proof}
  From Counterexamples: The irrationals are open, but contain no closed neighborhood, showing non-regular. Compact subsets are exactly finite subsets, showing non-$\sigma$-compact.

  Take open covers $\mc{U}_0,\mc{U}_1,\dots$. Define $\sigma(\mc{U}_0,\dots,\mc{U}_{2n})$ to be a finite subcover of $[-n,n]\setminus C_n$ for some countable $C_n=\{c_{n,0}, c_{n,1}, \dots\}$. For $\sigma(\mc{U}_0,\dots,\mc{U}_{2n+1})$, use any subcover of $\{c_{i,j} : i,j < n\}$. It is easily seen that $\sigma$ is a winning perfect information strategy.

  There cannot be a winning Markov strategy $\sigma(\mc{U},n)$, however. Define 
      \[
        D_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
      \]
  where $\mathfrak{C}$ is the collection of open covers of $R$. For any $x_0,x_1,\dots \in R$, we may define the open cover $\mc{U} = \{R \setminus \{x_i: i \not= n\} : n < \omega \}$, and observe that $\bigcup \sigma(\mc{U},n) \supseteq D_n$ cannot contain every $x_i$. Thus $D_n$ is finite, but since the previous lemma requires $\bigcup_{n<\omega} D_n = R$ if $\sigma$ is a winning strategy, there exists a counter to $\sigma$.
  \end{proof}

  \begin{theorem}
  For any topological space $X$ and all $k \geq 2$, $F \kmarkwin{k} \mengame{X}$ if and only if $F \kmarkwin{2} \mengame{X}$.
  \end{theorem}

  \begin{proof}
  Assume $\sigma(\mc{U}_0,\dots,\mc{U}_{k-1},n)$ is a winning $k$-Markov strategy. Define the $2$-Markov strategy $\tau(\mc{U},\mc{V},n)$ so that it contains $\sigma(\mc{W}_0,\dots,\mc{W}_{k-1},m)$ for the following conditions on $(\mc{W}_0,\dots,\mc{W}_{k-1},m)$:
    \begin{itemize}
    \item Each $\mc{W}_i \in \{\mc{U},\mc{V}\}$
    \item $m \leq (n+1)k$; in particular, for $i<k$, 
      \[
        \sigma(\mc{W}_0,\dots,\mc{W}_{k-1},(n+1)k+i)
        \subseteq 
        \tau(\mc{U},\mc{V},n+1) 
      \]
    \end{itemize}

  Considering an arbitrary play $\mc{U}_0, \mc{U}_1, \dots$ by $C$ versus $\tau$, we note that $\sigma$ defeats the play 
  \[
    \underbrace{\mc{U}_0,\mc{U}_0,\dots,\mc{U}_0}_{k},
    \underbrace{\mc{U}_1,\mc{U}_1,\dots,\mc{U}_1}_{k}
    \dots
  \]

  So we have that
    \[
      \bigcup_{i<k, n<\omega} \sigma(
      \underbrace{\mc{U}_n,\dots,\mc{U}_n}_{k-i-1},
      \underbrace{\mc{U}_{n+1},\dots,\mc{U}_{n+1}}_{i+1},
      (n+1)k+i)
    \]
  is a cover for $X$, and as 
    \[
      \sigma(
      \underbrace{\mc{U}_n,\dots,\mc{U}_n}_{k-i-1},
      \underbrace{\mc{U}_{n+1},\dots,\mc{U}_{n+1}}_{i+1},
      (n+1)k+i)
      \subseteq 
      \tau(\mc{U}_n,\mc{U}_{n+1},n+1)
    \]
  $\tau$ defeats the play $\mc{U}_0, \mc{U}_1, \dots$.
  \end{proof}

@@

  \begin{question}
    In general, does $F \markwin \mengame{X}$ imply $X$ is $\sigma$-compact?
  \end{question}
